---
title: "05-Workflows"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(AmesHousing)
library(tidymodels)
library(tune)
library(workflows)

ames <- make_ames() %>% 
  dplyr::select(-matches("Qu"))

set.seed(100)
ames_split <- initial_split(ames)
ames_train <- training(ames_split)
ames_test <- testing(ames_split)

fit_data <- function(object, model, data, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = "none", ...)))
  }
  fit(object, data, ...)
}

fit_split <- function(object, model, split, ...) {
  if (inherits(object, "formula")) {
    object <- add_model(add_formula(workflow(), object, blueprint = hardhat::default_formula_blueprint(indicators = "none")), model)
  }
  tune::last_fit(object, split, ...)
}

# pca_rec <- 
#   recipe(Sale_Price ~ ., data = ames) %>%
#     step_novel(all_nominal()) %>%
#     step_dummy(all_nominal()) %>%
#     step_zv(all_predictors()) %>%
#     step_center(all_predictors()) %>%
#     step_scale(all_predictors()) %>%
#     step_pca(all_predictors(), num_comp = 5)
```

# Checking "what could go wrong"

```{r}
ames_zsplit <- ames %>% 
  mutate(z_price = (Sale_Price - mean(Sale_Price)) / sd(Sale_Price)) %>% 
  initial_split()

ames %>% 
  mutate(z_price = (Sale_Price - mean(Sale_Price)) / sd(Sale_Price)) %>%
  select(Sale_Price, z_price)

ames %>% summarise(mean_price = mean(Sale_Price))
ames %>% summarise(sd_price = sd(Sale_Price))
ames %>% ggplot(aes(Sale_Price)) +
  geom_histogram() +
  geom_vline(xintercept = mean(ames$Sale_Price), color = "red")

rt_spec <- 
  decision_tree() %>%          
  set_engine(engine = "rpart") %>% 
  set_mode("regression")

set.seed(100) # Important!
fit_split(Sale_Price ~ Gr_Liv_Area, 
          model = rt_spec, 
          split = ames_zsplit) %>% 
  collect_metrics()

```


# Your Turn 1

Build a workflow that uses a linear model to predict `Sale_Price` with `Bedrooms_AbvGr`, `Full_Bath` and `Half_Bath` in `ames`. Save it as `bb_wf`.

```{r}
lm_spec <- 
  linear_reg() %>% 
  set_engine(engine = "lm") %>% 
  set_mode("regression")

bb_wf <- 
  workflow() %>% 
  add_model(spec = lm_spec) %>% 
  add_formula(Sale_Price ~ Bedrooms_AbvGr + Full_Bath + Half_Bath)

bb_wf
```


# Your Turn 2

Test the linear model that predicts `Sale_Price` with _everything else in `ames`_ on `ames_split`. What RMSE do you get?

Hint: Create a new workflow by updating `bb_wf`.

```{r}
all_wf <- 
  bb_wf %>% 
  update_formula(Sale_Price ~ .)

fit_split(all_wf, split = ames_split) %>% 
  collect_metrics()
```

# Your Turn 3

Fill in the blanks to test the regression tree model that predicts `Sale_Price` with _everything else in `ames`_ on `ames_split`. What RMSE do you get?

*Hint: Create a new workflow by updating `all_wf`.*

```{r}
rt_spec <- 
  decision_tree() %>%          
  set_engine(engine = "rpart") %>% 
  set_mode("regression")

rt_wf <- 
  all_wf %>% 
  update_model(spec = rt_spec)

fit_split(rt_wf, split = ames_split) %>% 
  collect_metrics()
```


# Your Turn 4

But what about the predictions of our model? Save the fitted object from your regression tree, and use `collect_predictions()` to see the predictions generated from the test data.

```{r}
all_fitwf <- fit_split(rt_wf, split = ames_split) 
  # tidyr::unnest(cols = .predictions)

preds <- all_fitwf %>% 
  collect_predictions()
preds

axis_lim <- range(c(preds$Sale_Price, preds$.pred))
ggplot(preds, aes(.pred, Sale_Price)) +
  geom_point() +
  xlim(axis_lim) + ylim(axis_lim) +
  coord_fixed() +
  geom_abline(slope = 1, intercept = 0, color = "blue")


all_fitwf %>% 
  pluck(".workflow", 1) %>% 
  pull_workflow_fit()

fitted_tree <- all_fitwf %>% 
  pluck(".workflow", 1) %>% 
  pull_workflow_fit() %>%
  pluck("fit")

```


